---
title: "HTML Document with Footer Template"
author: "Meera Y. Patel, M.D."
date: "`r Sys.Date()`"
output: 
  html_document:
    css: style.css
    theme: flatly
    highlight: kate  
    toc: yes
    number_sections: true
    toc_depth: 3 
    toc_float: 
      collapsed: false  
      smooth_scroll: false
    code_folding: show #or hide
    df_print: paged
    fig_height: 5 
    fig_width: 7 
    fig_caption: true
    dev: png
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "##",
                      tidy = TRUE, #`styler` to use styler:style_text() to reformat code
                      tidy.opts = list(blank = FALSE, width.cutoff = 60),
                      echo = TRUE,
                      eval = TRUE,
                      cache = FALSE,
                      cache.path = "reports/cache/",
                      child = NULL, #file/s to knit and then include,
                      collapse = FALSE, #collapse all output into a single block,
                      error = FALSE, #display error messages in doc. FALSE stops render when error is thrown
                      fig.align = "center", #left, right, center, or default
                      fig.width = 7, #inches
                      fig.height = 7, #inches
                      fig.asp=0.50, #adds whitespace around images
                      include = TRUE, #include chunk?
                      message = FALSE, #display code messages?
                      tidy = TRUE, #tidy code 
                      warning = FALSE, #include warnings?
                      results = "markup"
                        # "asis": passthrough results
                        # "hide": do not display results 
                        # "hold": put all results below all code
                      )
```
  
Installing the minimum required packages for setting up a new R Studio instance.  
The `secretary` package is installed for console messaging during the setup 
process. 

```{r,results='hide'}
if (!("devtools" %in% installed.packages()[,1])) {
  install.packages("devtools")
}
if (!("secretary" %in% installed.packages()[,1])) {
  devtools::install_github("meerapatelmd/secretary")
}
```

The list of packages to install is filtered for those that have not been 
installed yet. 

```{r}
packages_to_install <- 
  c(
  'aactR',
  'acepack',
  'amphora',
  'AsioHeaders',
  'askpass',
  'assertthat',
  'attempt',
  'automatonR',
  'backports',
  'base',
  'base64enc',
  'BH',
  'binman',
  'Biobase',
  'BiocGenerics',
  'BiocManager',
  'BiocVersion',
  'bit',
  'bit64',
  'bitops',
  'blob',
  'blogdown',
  'bookdown',
  'boot',
  'brew',
  'brio',
  'broca',
  'broom',
  'CallMeMaybe',
  'callr',
  'cancergovData',
  'caTools',
  'cave',
  'cellranger',
  'centipede',
  'chariot',
  'checkmate',
  'chemidplusData',
  'chemidplusSearchData',
  'class',
  'cli',
  'clinicalDataQuality',
  'clipr',
  'clisymbols',
  'cluster',
  'codetools',
  'collapsibleTree',
  'colorspace',
  'commonmark',
  'compiler',
  'condvis',
  'covr',
  'cpp11',
  'crayon',
  'credentials',
  'crosstalk',
  'curl',
  'data.table',
  'data.tree',
  'DatabaseConnector',
  'DatabaseConnectorJars',
  'datasets',
  'datasets.load',
  'DBI',
  'dbplyr',
  'desc',
  'devtools',
  'diffobj',
  'digest',
  'DistillerData',
  'downlit',
  'dplyr',
  'DT',
  'easyBakeOven',
  'ellipsis',
  'ETLSyntheaBuilder',
  'evaluate',
  'fansi',
  'farver',
  'fastmap',
  'fastmatch',
  'ff',
  'ffbase',
  'FHIRworks',
  'forcats',
  'foreign',
  'formatR',
  'Formula',
  'fs',
  'future',
  'future.apply',
  'gapminder',
  'gargle',
  'generics',
  'gert',
  'ggenealogy',
  'ggimage',
  'ggplot2',
  'ggplotify',
  'ggrepel',
  'gh',
  'git2r',
  'gitcreds',
  'glitter',
  'globals',
  'glue',
  'gmailr',
  'gmailrX',
  'gmp',
  'googledrive',
  'googlesheets',
  'googlesheets4',
  'graphics',
  'grDevices',
  'grid',
  'gridExtra',
  'gridGraphics',
  'gtable',
  'haven',
  'HemOncExt',
  'here',
  'hexbin',
  'hexSticker',
  'highlight',
  'highr',
  'Hmisc',
  'hms',
  'htmlTable',
  'htmltools',
  'htmlwidgets',
  'httpuv',
  'httr',
  'hunspell',
  'ids',
  'igraph',
  'ini',
  'isoband',
  'jpeg',
  'jsonld',
  'jsonlite',
  'kableExtra',
  'KernSmooth',
  'knitr',
  'labeling',
  'Lahman',
  'later',
  'lattice',
  'latticeExtra',
  'lazyeval',
  'leaflet',
  'leaflet.providers',
  'lifecycle',
  'listenv',
  'lubridate',
  'magick',
  'magrittr',
  'maps',
  'markdown',
  'MASS',
  'Matrix',
  'memoise',
  'metaorite',
  'metathesaurus',
  'methods',
  'mgcv',
  'microbenchmark',
  'mime',
  'miniUI',
  'modelr',
  'mOMOP',
  'munsell',
  'neo4r',
  'nlme',
  'nnet',
  'nycflights13',
  'officer',
  'OncoSeed',
  'ontologyIndex',
  'ontologyPlot',
  'ontologySimilarity',
  'openssl',
  'openxlsx',
  'packrat',
  'pagedown',
  'paintmap',
  'parallel',
  'parallelly',
  'pdftools',
  'pg13',
  'pillar',
  'pinp',
  'pkgbuild',
  'pkgconfig',
  'pkgdown',
  'pkgload',
  'plogr',
  'plotly',
  'plyr',
  'png',
  'police',
  'polite',
  'polyester2',
  'polyesterData',
  'postfixR',
  'praise',
  'preQL',
  'prettyunits',
  'processx',
  'progress',
  'promises',
  'pryr',
  'ps',
  'pubmedSearchData',
  'purrr',
  'qpdf',
  'R.cache',
  'R.methodsS3',
  'R.oo',
  'R.rsp',
  'R.utils',
  'r4ds',
  'R6',
  'ragg',
  'rappdirs',
  'raster',
  'ratelimitr',
  'rcmdcheck',
  'RColorBrewer',
  'Rcpp',
  'RcppArmadillo',
  'RCurl',
  'rdflib',
  'readi',
  'readr',
  'readxl',
  'redland',
  'rematch',
  'rematch2',
  'remotes',
  'reprex',
  'reshape2',
  'rex',
  'rJava',
  'rlang',
  'rmarkdown',
  'rMarkedDown',
  'RMySQL',
  'robotstxt',
  'rols',
  'roxygen2',
  'rpart',
  'rprojroot',
  'rsconnect',
  'RSelenium',
  'RSQLite',
  'rstudioapi',
  'rubix',
  'rvcheck',
  'rversions',
  'rvest',
  'scales',
  'seagull',
  'secretary',
  'selectr',
  'semver',
  'servr',
  'sessioninfo',
  'setupAthena',
  'setupMetathesaurus',
  'shiny',
  'showtext',
  'showtextdb',
  'sinew',
  'skyscraper',
  'sos',
  'sourcetools',
  'sp',
  'spatial',
  'spelling',
  'spiderbar',
  'splines',
  'SqlRender',
  'stampede',
  'stats',
  'stats4',
  'stringi',
  'stringr',
  'styler',
  'survival',
  'suzyBakeOven',
  'sys',
  'sysfonts',
  'systemfonts',
  'tcltk',
  'tesseract',
  'testthat',
  'textshaping',
  'tibble',
  'tidyr',
  'tidyselect',
  'tidyverse',
  'tinytex',
  'tools',
  'triebeard',
  'typewriteR',
  'uptodate',
  'urltools',
  'usethis',
  'utf8',
  'utils',
  'uuid',
  'V8',
  'vctrs',
  'viridis',
  'viridisLite',
  'vitae',
  'waldo',
  'wdman',
  'webshot',
  'websocket',
  'whisker',
  'withr',
  'WrapRmd',
  'xfun',
  'xlsx',
  'xlsxjars',
  'XML',
  'xml2',
  'xopen',
  'xtable',
  'yaml',
  'zip'
  )

installed_packages <- installed.packages()[,1]
packages_to_install <- 
  packages_to_install[!(packages_to_install %in% installed_packages)]

packages_to_install
```

An attempt to install each uninstalled package is made, with those returning an 
error saved to the `errors` vector. 

```{r,results='hide'}
errors <- vector()
for (i in seq_along(packages_to_install)) {
  secretary::typewrite(
    secretary::enbold(packages_to_install[i])
  )
  secretary::typewrite_progress(
    iteration = i,
    total = length(packages_to_install)
  )
  output <-
    tryCatch(
      expr = install.packages(packages_to_install[i]),
      error = function(e) "Error"
    )
  
  if (identical(output, "Error")) {
    
    errors <-
      c(errors,
        packages_to_install[i])
  }
}
```

The outstanding packages that returned as errors are retried as GitHub repos. 
```{r}
packages_to_install <- errors
packages_to_install
```

```{r,results='hide'}
errors <- vector()
for (i in 1:length(packages_to_install)) {
  secretary::typewrite(
    secretary::enbold(packages_to_install[i])
  )
  secretary::typewrite_progress(
    iteration = i,
    total = length(packages_to_install)
  )
  output <-
    tryCatch(
      expr = devtools::install_github(
        glue::glue("meerapatelmd/{packages_to_install[i]}"),
        build_vignettes = TRUE),
      error = function(e) "Error"
    )
  
  if (identical(output, "Error")) {
    errors <-
      c(errors,
        packages_to_install[i])
  }
}
```

